Graph Generators for Data Science: A Survey

### 2018-07-17 challenges.tex
Refactored graph streaming and community detection into others section
Added some braindump about open challenges

...

\subsection{Single- vs. multi-domain}
...

@@

%\paragraph{} Following the same recursion idea, paper~\cite{Leskovec:2005:RMT:2101235.2101254} uses Kronecker multiplication to generate self-similar graphs. The network starts with an initial graph G1 that contains $N_1$ nodes and $E_1$ edges. Using matrix recursion, larger successive graphs $G_2, G_3, ... G_n$ are generated. The $k$-th graph $G_k$ contains $N_k = N^k_1$ nodes. Many graphs often densify over time, exhibiting a growth in the number of edges that is superlinear to the number of nodes. Kronecker multiplication produces graphs with a fixed diameter and a densification power law degree distribution with exponent $k = log(E_1)/log(N_1)$. The graph generation process introduces a staircase effect in the nodes' degrees, and each community consists of smaller nested communities that are formed through expansion and recursion.

@@

\input{generators_community_detection}

>>>>

In this section, we discuss several of the open challenges in large scale graph
generation.

\subsection{Single- vs. multi-domain}

Most of existing graph generators generate graphs that are either not labeled or
are specific of a given domain (e.g.  Social Networks). Graphs from different
domains have different schemas, structural characteristics, property
distributions, etc. which might have an impact on the performance of the
application under test. Thus, graph processing engine developers are asking for
generators or tools to generate graphs flexibily, allowing to configure aspects
such as the size, the schema, the data distributions and other structural
characteristics such as the degree distribution, the clustering coefficient,
etc.

@@

%\paragraph{} Following the same recursion idea,
%paper~\cite{Leskovec:2005:RMT:2101235.2101254} uses Kronecker multiplication to
%generate self-similar graphs. The network starts with an initial graph G1 that
%contains $N_1$ nodes and $E_1$ edges. Using matrix recursion, larger successive
%graphs $G_2, G_3, ... G_n$ are generated. The $k$-th graph $G_k$ contains $N_k
%= N^k_1$ nodes. Many graphs often densify over time, exhibiting a growth in the
%number of edges that is superlinear to the number of nodes. Kronecker
%multiplication produces graphs with a fixed diameter and a densification power
%law degree distribution with exponent $k = log(E_1)/log(N_1)$. The graph
%generation process introduces a staircase effect in the nodes' degrees, and
%each community consists of smaller nested communities that are formed through
%expansion and recursion.

@@

\subsection{Large scale graphs with realistic structure}

Most of existing graph generators aiming at generating large graphs with realistic
structural characteristics focus principally on reproducing the degree
distribution and the clustering
coefficient~\cite{kolda2014scalable,edunov2016darwini}. However, there are other
structural characteristics one might be interested in reproducing for a large
graph, such the diameter, the size of the largest connected component, or the
hierarchical community structure. Graph practitioners are intersted in knowing
how other high-level structural characteristics affect the performance of graph
queries and graph algorithms. Thus, there is an open challenge to create
graph generators that allow reproducing many other structural characteristics
besides the degree or the clustering coefficient, that can also generat graphs
at a scale.

\subsection{Machine Learning based graph generation}

With the advent of neural networks and specially generative adversarial networks
(GANs)~\cite{goodfellow2014generative}, several researchers have started to
explore their application to generate graphs. This is the case of
~\cite{kipf2016variational,grover2018graphite,simonovsky2018graphvae,li2018learning,you2018graphrnn},
which present several generative models to generate realistic graphs.  Such
techniques still suffer from several problems. For instance, some of them are
limited to learn from a single
graph~\cite{kipf2016variational,grover2018graphite} or generate small
graphs~\cite{simonovsky2018graphvae,li2018learning,you2018graphrnn}. The
technique proposed in~\cite{you2018graphrnn} is capable of generating graphs
with complex edge dependencies (e.g. community structure) and is not restricted
to graphs of a fixed size. However, there is still in general several open
challenges, including the capability of learning from and generating large graphs comparable
in size to those typically used for benchmarking, and robust generation
techniques with structural guarantees (e.g. degree distribution, clustering
coefficient, etc.).
